---
title: "Deep Learning Image Classification with Keras"
author: "By Jasmine Dumas"
output: 
  flexdashboard::flex_dashboard:
    theme: simplex
    orientation: rows
    vertical_layout: fill
    runtime: shiny
    social: menu
    source_code: embed
---

```{r setup, include=FALSE}
library(devtools)
library(flexdashboard)
library(keras)
library(knitr)
library(DT)

options(DT.options = list(pageLength = 3, dom = 't'))
```


Sidebar {.sidebar}
=====================================

Keras is a user-friendly neural networks API. This application uses the **ResNet50 model**, with weights pre-trained on [ImageNet](http://www.image-net.org/) to enable fast experimentation for prediction of images classes including:

- Animals 🦋
- Plants 🌳
- Activities ⚽
- Food 🍹

______

```{r, sidebar}
# shiny inputs defined here
fileInput("file1", "Select an image from your local machine:", accept = c(".jpg", ".jpeg", ".png"))
```

Model {data-icon="fa-magic"}
=====================================  

Row {data-height=750}
-------------------------------------


### Image Preview

```{r}
renderImage({

  src <- input$file1
  src <- src$datapath

    if (is.null(src)) {
      list(src = "www/butterfly.jpg",
      height = "450",
      alt = "This is alternate text")
    } else {
      # Return a list
      list(src = src,
      height = "450",
      alt = "This is alternate text")
    }
      
  }, deleteFile = FALSE)
```


Row
-------------------------------------

### Results 

```{r, global, include=FALSE}
# instantiate the model
model <- application_resnet50(weights = 'imagenet')
```


```{r, results}
renderDT({
    # input$file1 will be NULL initially. After the user selects
    # and uploads a file, it will be a data frame with 'name',
    # 'size', 'type', and 'datapath' columns. The 'datapath'
    # column will contain the local filenames where the data can
    # be found.
    inFile <- input$file1

    if (is.null(inFile))
      return(NULL)

    withProgress(message = 'Predicting...', value = 1, {
      
    # load the image (copy an image from Photos)
    img_path <- inFile$datapath
    img <- image_load(img_path, target_size = c(224,224))
    x <- image_to_array(img)
    
    # ensure we have a 4d tensor with single element in the batch dimension,
    # the preprocess the input for prediction using resnet50
    x <- array_reshape(x, c(1, dim(x)))
    x <- imagenet_preprocess_input(x)
    
    # make predictions then decode and print them
    preds <- model %>% predict(x)
    
    # table mods
    main = imagenet_decode_predictions(preds, top = 3)[[1]]
    main$explore_class_on_imagenet <- sprintf('<a href="http://image-net.org/explore?wnid=%s" target="_blank">Explore %s on ImageNet</a>', main$class_name, main$class_description)
    
    DT::datatable(main)
    
    return(main)
  }) # end of progress message
}, escape = FALSE)
```
   


Resources {data-icon="fa-bookmark"}
===================================== 

**What the heck is a Deep Learning model?**

A Deep Learning model (neural net/work) is essentially a bunch of linear models stitched together, capable of abstracting complex non-linear relationships from the training data. These models allow for the modeler to focus on hyper parameter tuning instead of feature engineering.

**What is a pre-trained model?**

A pre-trained model is one which has been previously trained on a similar task other than the current one. It has two parts – model architecture and model weights. 

**What are the benefits and tradeoffs?**

A pre-trained model, while not 100% accurate still provides a very useful starting point because the features learned while training on the former task are useful for the new task. [4]  
Tranfering the learnings from the pre-trained model reduces the computational cost from developing a neural net from scratch. 

_____
  
Here are a list of tutorials and papers about Deep Learning & Image Classification:
  
1. [DataCamp's Keras Deep Learning R Tutorial](https://www.datacamp.com/community/tutorials/keras-r-deep-learning)
2. [Deep Residual Learning for Image Recognition](https://arxiv.org/abs/1512.03385)  
3. [ResNet50 Model](http://ethereon.github.io/netscope/#/gist/db945b393d40bfa26006)
4. [Keras Tutorial: Using pre-trained Imagenet models](http://www.learnopencv.com/keras-tutorial-using-pre-trained-imagenet-models/)
5. [Keras Pretrained models from Kaggle](https://www.kaggle.com/gaborfodor/keras-pretrained-models)
6. [Transfer learning & The art of using Pre-trained Models in Deep Learning](https://www.analyticsvidhya.com/blog/2017/06/transfer-learning-the-art-of-fine-tuning-a-pre-trained-model/)
7. [useR 2016 Machine Learning Algorithmic Deep Dive Tutorial](https://github.com/ledell/useR-machine-learning-tutorial/blob/master/deep-neural-networks.ipynb)
8. [Transfer Learning](https://en.wikipedia.org/wiki/Transfer_learning)


